The Splashback Radius of Planck-SZ clusters

### 2019-01-25 Paper_v2/RSP_paper_new.tex
Reviewing Surhuds corrections

\textbf{To avoid optical cluster selection effects, there have been some
previous efforts to use X-ray selected cluster samples to look for the
splashback radius using the weak lensing signal\{umetsu2017lensing,
contigiani2018weak}}.  However stacking issues and the low signal-to-noise
ratio remains a significant hurdle for both of them. \textbf{The use of weak
lensing in these studies could get around the biased nature of the galaxy
distribution by directly probing the dark matter distribution. Along those
lines,} \citet{chang2017splashback} found evidence for the splashback feature
in the weak lensing signal, but their analysis was again done using optically
selected clusters in the Dark energy survey that suffer from the
afore-mentioned issues.

@@

\textbf{Dynamical friction is expected to slow down massive subhalos, hosting
galaxies that are orbiting the galaxy cluster XXXX{Cite paper by Chandrasekhar
here}XXXX. If a majority of the observed galaxies are hosted by these massive
subhalos, the slow down due to dynamical friction would reduce the apocenters
of their orbits, in turn, biasing the measured splashback radius of the host
cluster XXX{Cite More2016 and papers on Benedikt's SPARTA}XXX. As dynamical
friction timescales are inversely proportional to the mass of the subhalos,
this effect is stronger for more massive subhalos. Therefore, one expects the
splashback radius to decrease for more massive subhalos
\citep{adhikari2016observing}.  This bias can be limited by choosing a faint
galaxy sample such that majority of the galaxies reside in low mass subhalos,
unaffected by dynamical friction.} The SDSS sample used by
\citet{more2016detection} was already deep enough such that biases in the
location of the splashback radius due to dynamical friction effects were
expected to be small. Nevertheless, we use galaxy samples, which are fainter by
$0.5-1$ magnitudes compared to those used by \citet{more2016detection}.

@@

\textbf{The location of the splashback radius can be identified in various
ways, e.g., as the radius of the outermost shell in theoretical models of
spherical symmetric collapse \citep{adhikari2014splashback, shi2016outer}, or
using non-spherical shells of density jumps \citet{ mansfield2017splashback},
or the average location of the apocenter of particles falling in the cluster
potential \citet{diemer2017splashback}. Although these definitions have subtle
differences, they all follow the general trend of a decreasing splashback
radius with increasing rate of accretion XXX{Cite Benedikt and Phils paper for
these comparisons}. In this paper, we adopt the convention of
\citet{more2015splashback}, who define the location of the splashback radius
for halos on galaxy cluster scales to be the location of the steepest
logarithmic slope of the radially averaged density profile, due to its ease of
accessibility in data.}

>>>>

\textbf{To avoid optical cluster selection effects, there have been some
previous efforts to use X-ray selected cluster samples to look for the
splashback radius using the weak lensing signal \citep{umetsu2017lensing,
contigiani2018weak}}. However stacking issues and the low signal-to-noise
ratio remains a significant hurdle for both of them. \textbf{The use of weak
lensing data in these studies could get around the biased nature of the galaxy
distribution by directly probing the dark matter distribution. Along those
lines,} \citet{chang2017splashback} found evidence for the splashback feature
in the weak lensing signal, but their analysis was again done using optically
selected clusters in the Dark energy survey that suffer from the
afore-mentioned issues.

@@

\textbf{Dynamical friction is expected to slow down massive subhalos, hosting
galaxies that are orbiting the galaxy cluster \citep{chandrasekhar1943dynamical}.
If a majority of the observed galaxies are hosted by these massive
subhalos, the slow down due to dynamical friction would reduce the apocenters
of their orbits, and in turn, biasing the measured splashback radius of the host
cluster \citep{more2016detection, diemer2017sparta}. As dynamical
friction timescales are inversely proportional to the mass of the subhalos,
this effect is stronger for more massive subhalos. Therefore, one expects the
splashback radius to decrease for more massive subhalos
\citep{adhikari2016observing}.  This bias can be limited by choosing a faint
galaxy sample such that the majority of the galaxies reside in low mass subhalos,
unaffected by dynamical friction.} The SDSS sample used by
\citet{more2016detection} was already deep enough such that biases in the
location of the splashback radius due to dynamical friction effects were
expected to be small. Nevertheless, we use galaxy samples, which are fainter by
$0.5-1$ magnitudes compared to those used by \citet{more2016detection}.

@@

\textbf{The location of the splashback radius can be identified in various
ways, e.g., as the radius of the outermost shell in theoretical models of
spherical symmetric collapse \citep{adhikari2014splashback, shi2016outer}, or
using non-spherical shells of density jumps \citep{ mansfield2017splashback},
or the average location of the apocenter of particles falling in the cluster
potential \citet{diemer2017splashback}. Although these definitions have subtle
differences, they all follow the general trend of a decreasing splashback
radius with increasing rate of accretion \citep{diemer2017splashback}.
In this paper, we adopt the convention of
\citet{more2015splashback}, who define the location of the splashback radius
for halos on galaxy cluster scales to be the location of the steepest
logarithmic slope of the radially averaged density profile, due to its ease of
accessibility in data.}
